\documentclass[10pt,a4paper]{article}
\usepackage[top = 2cm, bottom = 2cm, left = 2cm, right = 2cm]{geometry}

% Mathematical packages
\usepackage{amsmath, amssymb, amsfonts, amsthm}
\usepackage{bm}

% Graphical packages
\usepackage{graphicx}
\graphicspath{{graphics/}}
\usepackage{xcolor}
\definecolor{darkgreen}{rgb}{0.04, 0.30, 0.00}

% Fonts
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
%\usepackage[utf8]{inputenc}

% Endnotes, enumeration
\usepackage{endnotes}
\usepackage{enumitem}

% Parts, sections, subsections ...
\usepackage{titlesec}
\titleformat{\section}{\normalfont\huge\bfseries}{Chapter \thesection}{-5em}{\Huge\newline}

% fbox

% Theorem, definition, lemma, postulate ....
\newcounter{numtheorem}

\newcommand{\theorem}[2]{
    \refstepcounter{numtheorem}
    \color{blue}
    \noindent\fbox{\textbf{1.\thenumtheorem }} \textbf{#1:}
    \color{black}
    #2\newline
}

\newcommand{\definition}[2]{
    \refstepcounter{numtheorem}
    \color{darkgreen}
    \noindent\fbox{\textbf{1.\thenumtheorem }} \textbf{#1:}
    \color{black}
    #2\newline
}

\newcommand{\note}[2]{
    \refstepcounter{numtheorem}
    \color{gray}
    \noindent\fbox{\textbf{1.\thenumtheorem }} \textbf{#1:}
    \color{black}
    #2\newline
}

\newcommand{\remark}[2]{
    \refstepcounter{numtheorem}
    \color{orange}
    \noindent\fbox{\textbf{1.\thenumtheorem }} \textbf{#1:}
    \color{black}
    #2\newline
}

\newcommand{\problem}[2]{
    \refstepcounter{numtheorem}
    \color{darkred}
    \noindent\fbox{\textbf{1.\thenumtheorem }} \textbf{#1:}
    \color{black}
    #2\newline
}

\newcommand{\exmpl}[2]{
    \refstepcounter{numtheorem}
    \color{red}
    \noindent\fbox{\textbf{1.\thenumtheorem }} \textbf{#1:}
    \color{black}
    #2\newline
}

\renewcommand{\proof}[1]{%
    \noindent\textbf{Proof:}~#1%
    \newline%
    \strut\hfill%
    $\square$%
    \newline%
}%

\renewcommand\d{\mathrm d}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}

\setlength\parindent{0pt}

\begin{document}

\tableofcontents
~\newpage

\section{Topology}

The notion of topology gives sense to the intuitive ideas of nearness and continuity. It appears that there are equivalent ways of defining a topology: In terms of open sets, or of closed sets or using as primitive notion the notion of neighbourhood of a point.

\subsection{Preliminaries}

\theorem{De Morgan's laws}{
    Let $A,B\subset X$. Then
    \[C_X\left(A\cup B\right)=C_X A\cap C_X B\]
    \[C_X\left(A\cap B\right)=C_X A\cup C_X B\]
    where $C_XA=\{x\in X|x\notin A\}$ denotes the complement of $A$.
}
\\
\proof{
To proof that $C_X\left(A\cup B\right)=C_X A\cap C_X B$ is completed in 2 steps by proving both $C_X\left(A\cup B\right)\subseteq C_X A\cap C_X B$ and $C_X\left(A\cup B\right)\supseteq C_X A\cap C_X B$.\\\\
\textbf{Part 1:}
Let $x\in C_X(A\cap B)$, then $x\notin A\cap B$.
Because $A\cap B=\{\,y\,|\,y\in A\wedge y\in B\,\}$, it must be the case that $x\notin A$ or $x\notin B$.
If $x\notin A$, then $x\in C_XA$, so $x\in C_XA\cup C_XB$.
Similary, if $x\notin B$, then $x\in C_XB$, so $x\in C_XA\cup C_XB$.
Hence, $\forall x: x\in C_X(A\cap B)\Rightarrow x\in C_XA\cup C_XB$, that is, $C_X\left(A\cup B\right)\subseteq C_X A\cap C_X B$.\\\\
\textbf{Part 2:}
To prove the reverse direction, let $x\in C_XA\cup C_XB$, and for contradiction assume $x\notin C_X(A\cap B)$. Under that assumption, it must be the case that $x\in A\cap B$, so it follows that $x\in A$ and $x\in B$, and thus $x\notin C_XA$ and $x\notin C_XB$. However, that means $x\notin C_XA\cup C_XB$, in contradiction to the hypothesis that $x\in C_XA\cup C_XB$ therefore, the assumption $x\notin C_X(A\cap B)$ must not be the case, meaning that $x\in C_X(A\cap B)$.
Thus, $\forall x: x\in C_XA\cup C_XB\Rightarrow x\in C_X(A\cap B)$ , that is, $C_X\left(A\cup B\right)\supseteq C_X A\cap C_X B$.\\
}

\subsection{Topological spaces}

\definition{Definition}{
    A \textbf{topological space} is a non-empty set $X$ together with a family $\tau=\left(U_i\;|\;\forall i\in I, U_i\subset X\right)$\\("of subsets of $X$") satisfying the following axioms:

    \begin{enumerate}
        \item $\emptyset,X\in\{\tau\}$
        \item The intersection of any finite number of sets in $\tau$ belongs to $\tau$, i.e.
        \[
            J\text{ finite },J\subset I\Rightarrow\bigcap_{i\in J}U_i\in\tau
        \]
        \item The union of any number of sets in $\tau$ belongs to $\tau$, i.e.
        \[
            J\subset I\Rightarrow\bigcup_{i\in J}U_i\in\tau
        \]
    \end{enumerate}
    The elements of $\tau$ are called $\tau$-open sets, or simply open sets in $X$. The pair $(X, \tau)$ is called a topological space.
}

\exmpl{Example}{
    The family $\{\tau\}=\{\emptyset,X\}$, consisting of $\emptyset$ and $X$ alone is itself a topology called the \textbf{indiscrete topology}. $\{\emptyset,X\}$ is then called an indiscrete topological space.
}

\exmpl{Example}{
    Let $\tau=P\left(X\right)$ denote the family of all subsets of $X$ (power set). Observe that $P\left(X\right)$ satisfies the axioms 1.-3. for a topology on $X$. This topology is called the \textbf{discrete topology}, the pair $\{X,P\left(X\right)\}$ is called a discrete topological space.
}

\exmpl{Example}{
    Let $X=\R$ be the real line. A topology on $\R$ can be defined as follows: For any $x\in\R$, consider the open intervals $\left(a, b\right)$ containing $x$, then $\tau$ is the family
    \[
        \tau=\{U_i=(a_i,b_i)\;|\;a_i,b_i\in\R\;,a_i\leq b_i\}
    \]
    If $a_i=b_i$, then $(a_i,b_i)=\emptyset$. This topology is referred as the \textbf{usual topology} on $\R$. Similarly, one can define the usual topology on $\R^n$.
}

\definition{Definition}{
     Let $(X, \tau)$ be a topological space. A subset $A$ of $X$ is \textbf{closed} if its complement $C_XA$ is an open set.
}

\theorem{Theorem}{
The family $\overline\tau=\left(A_i\;|\;\forall i\in I\right)$ of closed subsets of $X$ satisfying the following conditions:

\begin{enumerate}
    \item $\emptyset$ and $X$ are closed sets, i.e. $\emptyset,X\in\overline\tau$
    \item The union of any finite number of sets in $\overline\tau$ belongs to $\overline\tau$, i.e.
    \[
        J\text{ finite },J\subset I\Rightarrow\bigcup_{i\in J}U_i\in\overline\tau
    \]
    \item The intersection of any number of sets in $\overline\tau$ belongs to $\overline\tau$, i.e.
    \[
        J\subset I\Rightarrow\bigcap_{i\in J}U_i\in\overline\tau
    \]
\end{enumerate}
We denote this topological place $(X, \overline\tau)$.
}
\\
\proof{
 Follows from De'Morgan laws and definition of the topological space of the open sets.
}

\subsection{Neighbourhood spaces}

\definition{Definition}{
    Let $x\in X$ be a point in a topological space $X$. Any subset $U$ of $X$ containing an open set $A$ such that $x\in A$ is called a \textbf{neighbourhood} of $x$ denoted by $U=U(x)$. In particular, any open set $U$ is a neighbourhood of each of its points. The class of all neighbourhoods of $x\in X$, denoted by $\mathfrak B(x)$, is called the \textbf{fundamental neighbourhood system} of $x$.
}

\subsection{Types of points}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. A point $x\in A$ is said to be an \textbf{isolated point} of $A$ if there exists an open set containing $x$ which contains no other points of $A$.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. A point $x\in A$ is said to be an \textbf{accumulation point} of $A$ if every open set containing $x$ contains at least one other point from $A$. (Basically the opposite to the isolated point of $A$).
}

\definition{Definition}{
    Let $(X,\{\tau\})$ be a topological space and $A\subset X$. A point $x\in X$ is said to be an \textbf{adherent point} of $A$ if every neighbourhood of $x$ contains at least one other point of $A$.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. A point $x\in X$ is said to be a \textbf{limit point} of $A$ if every neighbourhood of $x$ contains infinitely many points of $A$.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. A point $x\in X$ is said to be a \textbf{condensation point} of $A$ if every neighbourhood of $x$ contains uncountable1 many points of $A$.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. A point $x\in X$ is said to be a \textbf{interior point} of $A$ if there exists an open set $U$ containing $x$ that is completely a subset of $A$.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. A point $x\in X$ is said to be a \textbf{boundary point} of $A$ if every neighbourhood of $x$ contains at least one point of $A$ and at least one point of $C_XA$.
}

\remark{Remark}{
    Isolated and accumulation points of $A$ are always in $A$, while adherent, limit and condensation points don't have to be in $A$. If a point is isolated it can't be accumulated and vice versa. Every interior point of $A$ is also a condensation point of $A$, every condensation point of $A$ is also a limit point of $A$, and every limit point of $A$ is also an adherent point of $A$. Isolated and accumulation points are both adherent but can't be limit or condensation points.
}

\theorem{Theorem}{
    Union of set of interior points and boundary points is a set of adherent points.
}

\exmpl{Example}{
    The set $\N$ in usual topology on $\R$ has no accumulation point, i.e. all points of $\N$ are isolated.
}

\exmpl{Example}{
    The set $A=(0,1]\cup\{2\}\subset\R$ which has the usual topology on $\R$ has limit point every point of the interval $[0,1]$. Notice that 2 is an isolated nonlimit point and 0 is a limit point but does not belongs to $A$.
}

\definition{Definition}{
    The set of all limit points of $A$, denoted by $A'$ is called the \textbf{derived set} of $A$.
}

\exmpl{Example}{
    Discrete topology where adherent points are not limit points.
}

\subsection{Closure}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. A point $x\in X$ is said to be an \textbf{adherent point} of $A$ if every neighbourhood of $x$ contains at least one other point of $A$.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. The set of all adherent points of $A$, denoted by $\overline A$, is called a \textbf{closure} of $A$.
}

\theorem{Theorem}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. The closure of a set $A$ is the intersection of all closed supersets of $A$ and $\overline A$ is the smallest closed superset of $A$.
}

\proof{
    Let $(U|i\in I)$ be the family of all closed supersets of $A$. If $x\in\overline A$, then $x$ is adherent point and belongs to a closed superset of $A$, i.e. $\exists i_0\,:\,x\in U_{i_0}$. Hence $x\in\bigcap_i U_i$ and $\overline A\subset\bigcap_i U_i$. Conversely, $y\in\bigcap_i U_i$, implies $y\in U_i$ for every $i$. Thus $y$ is an adherent point, i.e $y\in\overline A$ and if we take all such $y$ we have $\bigcap_i U_i\subset\overline A$. Accordingly $\overline A=\bigcap_i U_i$, while not forgetting axiom: intersection of closed sets is a closed set, hence $\overline A$ is closed. If $U$ is a closed superset of $A$, it is in the family $(U|i\in I)$ and because $\closed A=\bigcap_i U_i$ we have $\overline A\subset U$.
}

\theorem{Theorem}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. Every point of a closed set $A$ is its adherent point, i.e $A=\overline A$.
}

\proof{
    Because $\overline A$ is the intersection of all closed supersets of $A$ we have $A\subset\overline A$. But if $A$ is closed and $\overline A$ is the smallest closed superset of $A$ then $\overline A\subset A$. Therefore $A=\overline A$.
}

\exmpl{Example}{
    The empty set $\emptyset$ is closed, since there is no point in $\empty$ which is not an accumulation point. And as every accumulation point is also adherent we have $\overline\emptyset=\emptyset$.
}

\subsection{Interior}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. A point $x\in X$ is said to be a \textbf{interior point} of $A$ if there exists an open set $U$ containing $x$ that is completely a subset of $A$.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. The set of all interior points of $A$, denoted by $\mathring A$, is called an \textbf{interior} of $A$.
}

\theorem{Theorem}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. The interior of a set $A$ is the union of all open subsets of $A$ and $\mathring A$ is the largest open subset of $A$.
}

\proof{
    Let $(U|i\in I)$ be the family of all open subsets of $A$. If $x\in\mathring A$, then $x$ is interior point and belongs to an open subset of $A$, i.e. $\exists i_0\,:\,x\in U_{i_0}$. Hence $x\in\bigcup_i U_i$ and $\mathring A\subset\bigcup_i U_i$. Conversely, $y\in\bigcup_i U_i$, implies $y\in U_i$ for some $i$. Thus $y$ is an interior point, i.e $y\in\mathring A$ and if we take all such $y$ we have $\bigcup_i U_i\subset\mathring A$. Accordingly $\mathring A=\bigcup_i U_i$, while not forgetting axiom: uion of open sets is an open set, hence $\mathring A$ is open. If $U$ is an open subset of $A$, it is in the family $(U|i\in I)$ and because $\mathring A=\bigcup_i U_i$ we have $U\subset\mathring A$.
}

\theorem{Theorem}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. Every point of an open set $A$ is its interior point, i.e $A=\mathring A$.
}

\proof{
    Because $\mathring A$ is the union of all open subsets of $A$ we have $\mathring A\subset A$. But if $A$ is open and $\mathring A$ is the largest open subset of $A$ then $A\subset\mathring A$. Therefore $A=\mathring A$.
}

\subsection{Boundary}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. A point $x\in X$ is said to be a \textbf{boundary point} of $A$ if every neighbourhood of $x$ contains at least one point of $A$ and at least one point of $C_XA$.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. The set of all boundary points of $A$, denoted by $\partial A$, is called a \textbf{boundary} of $A$.
}

\theorem{Theorem}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. The set $A$ is said to be closed subset of $X$ $\Leftrightarrow$ $A$ contains all of its boundary points.
}

\proof{
    First assume $A$ is closed. Assume, for a contradiction, that there is $x\in\partial A$ such that $x\notin A$. Then $x\in C_XA$ which is open so there exists an open set $U$ containing $x$ that is entirely in $C_XA$. Then this set contains no points in $A$ contradicting the definition of the boundary point $x$.\\\\
    Now assume that all $x$ from $\partial A$ are also in $A$. Assume, for a contradiction, that $A$ is open. If $A$ is open, then for every point of $A$ exists an open set $U$ eentirely in $A$. But then there is no point satisfying the definition of boundary point and we arrive to contradiction.
}

\theorem{Theorem}{
    Let $(X,\tau)$ be a topological space and $A\subset X$. The set $A$ is said to be open subset of $X$ $\Leftrightarrow$ $A$ does not contain any of its boundary points.
}

\proof{
    If $A$ is open, then for every point of $A$ exists an open set $U$ eentirely in $A$. But then there is no point satisfying the definition of boundary point, hence $A$ does not contain any of its boundary points.\\\\
    Now assume that $A$ does not contain any of its boundary points. Assume, for a contradiction, that $A$ is closed. But we already proved that closed set contains all of its boundary points, therefore we arrive to contradiction.
}

\theorem{Theorem}{
    Let $(X,\{\tau\})$ be a topological space and $A\subset X$. The boundary of a set $A$ is given by $\partial A=\overline A\backslash\mathring A$. Furthermore $\overline A=\mathring A\cup\partial A$ and $A=\partial A\Leftrightarrow\mathring A=\emptyset$.
}

\exmpl{Example}{
    Consider the usual topology on $\R$ and the set $\Q$ of rational numbers. Every real number $x\in\R$ is an adherent point of $\Q$, {\color{red}WHY?}. Moreover, $\mathring\Q=\left(C_\R\Q\right)\mathring{}=\emptyset$, since every open subset of $\R$ contains both rational and irrational points, hence there are no interior points of $\Q$ and $C_\R\Q$, furhtemore $\partial\Q=\overline\Q\backslash\mathring\Q=\R$.
}

\subsection{Continuous maps}

\definition{Definition}{
    Let $(X_i,\tau_i)$, $i=1,2$, be topological spaces. A map $f:X_1\to X_2$ is \textbf{continuous} at a point $x_0\in X_1$ if for any neighborhood $V(f(x_0))$ of $f(x_0)$ there exists a neighborhood $U(x_0)$ of $x_0$ such that $f(U)\subset V$, i.e.
    \[
        f\text{ is continuous at }x_0\in X_1\Leftrightarrow\forall V(f(x_0))\,\exists U(x_0)\,:\,f(U(x_0))\subset V(x_0).
    \]
}

\definition{Definition}{
    Let $(X_i,\tau_i)$, $i=1,2$, be topological spaces. A map $f:X_1\to X_2$  is called an \textbf{open map} if, for any open set $U\subset X_1$, $f(U)$ is an open set in $X_2$.
}

\definition{Definition}{
    Let $(X_i,\{\tau\}_i)$, $i=1,2$, be topological spaces and $f:X_1\to X_2$ a map. Let $U\in X_2$ and denote $f^{-1}(U)=\{x\in X_1|f(x)\in U\}$.
}

\definition{Definition}{
    Two topological spaces $(X_i,\{\tau\}_i)$, $i=1,2$, are called \textbf{homeomorphic} if there exists a bijective map $f:X_1\to X_2$ such that $f$ and $f^{-1}$ are continuous. The map $f$ is called a \textbf{homeomorphism}.
}

\subsection{Properties of topological spaces}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space. $(X,\tau)$ is a \textbf{Hausdorff space} if it satisfies the following additional axiom: For every pair of distinct points $x_1,x_2\in X$ there are disjoint neighborhoods $U_1(x_1),U_2(x_2)$, i.e:
    \[
        \forall x_1,x_2\in X, x_1\neq x_2,\;\exists U_1(x_1),U_2(x_2)\,:\,U_1(x_1)\cap U_2(x_2)=\emptyset.
    \]
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space. A \textbf{base} for the topology $\tau$ of a topological space $(X, \tau)$ is a family $\mathfrak B$ of open subsets of $X$ such that every open set is equal to a union of sets from $\mathfrak B$.
}

\definition{Definition}{
    A topological space $(X,\tau)$ is called \textbf{second countable}, if there exist a countable base $\mathfrak B$ for the topology $\tau$.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space. A family $\mathfrak U =(A_i|i\in I)$ of subsets of $X$ is called a \textbf{cover} of $X$, if
    \[
        \forall i\in I:\,A_i\neq\emptyset
    \]
    \[
        X=\bigcup_{i\in I}A_i
    \]
    If, for $J\subset I$, $X=\bigcup_{j\in J}A_j$, then $(A_j|j\in J)$ is called a \textbf{subcover}. In particular it is a \textbf{finite subcover} if the index set $J$ is finite.
}

\definition{Definition}{
    A topological space $(X,\tau)$ is \textbf{compact}, if every open cover of $X$ has a finite subcover.
}

\definition{Definition}{
    Let $(X,\tau)$ be a topological space. A set $S\subset X$ is \textbf{compact}, if every open cover of $S$ has a finite subcover.
}

\note{Note}{
    Some authors require that a compact topological space be Hausdorff as well, and use the term quasi-compact to refer to a non-Hausdorff compact space. The modern convention seems to be to use compact in the sense given here.
}

\theorem{A compact subset of a Hausdorff space is closed}{
    Suppose $X$ is a Hausdorff space. If $K$ is a compact subset of $X$, then $K$ is a compact set in $X$.
}

\proof{
    Let $X$ be a Hausdorff space, and $S\subset X$ a compact subset. To show that $S$ is closed, its enough to show that the complement $U=C_XS=X\backslash S$ is open. For $U$ to be open is sufficient to demonstrate that for each $x\in U$, there exists an open set $V$ with $x\in V$ and $V\subset U$.\\

    Fix $x\in U$. For each $y\in S$, using the definition of Hausdorff space, we can choose disjoint open sets $A$ and $B$ with $x\in A(y)$ and $y\in B(y)$.\\

    Since every $y\in S$ is an element of $B(y)$, the family $\{B(y)\,|\,y\in S\}$ is an open cover of $S$. Since $S$ is compact, this open cover has a finite subcover. Therefore we can choose $y_1,\ldost,y_n\in S$ such that $S\subset B(y_1)\cup\dots\cup B(y_n)$.\\

    Notice that $A(y_1)\cap\dots\cap A(y_n)$, being a finite intersection of open sets, is open, and contains $x$. Call this neighborhood of $x$ by the name $V$. All we need to do is show that $V\subset U$.\\

    For any point $z\in S$, we have $z\in B(y_1)\cup\dots\cup B(y_n)$, and therefore $z\in B(y_k)$ for some $k$. Since $A(y_k)$ and $B(y_k)$ are disjoint, $z\notin A(y_k)$, and therefore $z\notin A(y_1)\cap\dots\cap A(y_n)=V$. Thus $S$ is disjoint from $V$, and $V$ is contained in $U$.
}

\remark{Remark}{
    This theorem is giving us closed intervals as we know them in $\R$ to use in all Hausdorff spaces. But this time closed means compact.
}

\definition{Definition}{
    Lt $\{X,\tau\}$ be a topological space. A family $A=\{A_i\}_{i\in I}$ of subsets of a set $X$ is said to have the \textbf{finite intersection property}, if every finite subfamily $\{A_1,A_2,\ldots.A_n\}$ of $A$ satisifes $\bigcap_{i=1}^nA_i\neq\emptyset$.
}

\exmpl{Example}{
    Consider $\R$ as a topological space with usual topology, then the family of closed intervals\\ $A=\big\{\left[n+\frac{1}{n},n+1-\frac{1}{n}\right]\,\big|\,n\in\N\big\}$ does not have the finite intersection property, howerer for $n\to\infty$ the intervals will touch, hence intersect.
}

\theorem{Theorem}{
    A topological space $\{X,\tau\}$ is compact if and only if for every family $A=\{A_i\}_{i\in I}$ of closed subsets of $X$, where $A$ has the finite intersection property, $\bigcap_{i=1}^nA_i=\emptyset$.
}

\proof{
    Let $\{X,\tau\}$ be a topological space and assume that the intersection of any family of closed subsets having the finite intersection property is non-empty. Let $\{F_i\}_{i\in I}$ be some open cover of $X$ and assume that it has no finite subcover. Hence for each finite $J\subseteq I$ there is some $x\in X$ such that $x\notin \bigcup_{i\in J}F_i$. Equivalently, for each finite $J\subseteq I$ there is some $x\in\bigcap_{i\in J}C_XF_i$. Hence the family $\{C_XF_i\}_{i\in I}$ is a family of closed subsets with the finite intersection property. It follows that there is some $x\in\bigcap_{i\in I}C_XF_i$, i.e., $x\notin \bigcup_{i\in I}F_i$, contradicting that $\{F_i\}_{i\in I}$ is a cover of $X$. We conclude that $\{F_i\}_{i\in I}$ must have a finite subcover, so $X$ is compact.\\

    The proof in the other direction is analogous. Conversely, assume that $X$ is compact and let $\{F_i\}_{i\in I}$ be some family of closed subsets with the finite intersection property. Assume that $\bigcap_{i\in I}F_i$ is empty. Then $\{C_XF_i\}_{i\in I}$ is an open cover of $X$. By compactness, it has a finite subcover, so $\bigcup_{i\in J}C_XF_i=X$ for some finite $J\subseteq I$. But then $\bigcup_{i\in J}F_i=\emptyset$, contradicting that $\{F_i\}_{i\in I}$ has the finite intersection property. We conclude that $\bigcap_{i\in I}F_i\new\emptyset$, i.e .
}

\remark{Remark}{
    One can understnad this theorem as every family $A$ has to have also the "infinite" intersection property.
}

\remark{Remark}{
    The above theorem is essentially the definition of a compact space rewritten using de Morgan’s laws. The usual definition of a compact space is based on open sets and unions. The above characterization, on the other hand, is written using closed sets and intersections.
}

\exmpl{Example}{
    Consider $\R$ as a topological space with usual topology, then the family of open intervals \\ $A=\big\{\left(n-\frac{1}{n},n+1+\frac{1}{n}\right)\,\big|\,n\in\N\big\}$ has the finite intersection property, howerer for $n\to\infty$ the intervals will stop intersecting, hence $\R$ is not compact.
}

\theorem{A closed subset in a compact space is compact}{
    Suppose $\{X,\tau\}$ is a topological space. Let $C\subset K\subset X$ where $C$ is closed relative to $K$ and $K$ is compact. Then $C$ is compact.
}

\proof{
    Suppose $C$ is not compact. Then there is a cover of $C$ which has no finite subcover say, call this cover $S$. Define $M=X\backslash C$. Then $M\cup S$ is a cover of $K$. But then clearly, this cover has no finite subcover hence $K$ is not compact.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. Space $X$ is called \textbf{locally compact} if every point $x$ of $X$ has a compact neighbourhood, i.e., there exists an open set $U\subset X$ and a compact set $K\subset X$, such that $x\in U\subseteq K$.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. A \textbf{refinement} of a cover of a space $X$ is a new cover of the same space such that every set in the new cover is a subset of some set in the old cover. I.e., the cover $V=\{V_\beta:\beta\in B\}$ is a refinement of the cover $U=\{U_\alpha:\alpha\in A\}$ if and only if, for any $V_\beta$ in $V$, there exists some $U_\alpha$ in $U$ such that $V_\beta\subseteq U_\alpha$.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. An open cover of a space $X$ is \textbf{locally finite} if every point of the space has a neighborhood that intersects only finitely many sets in the cover. I.e., $U=\{U_\alpha:\alpha\in A\}$ is locally finite if and only if, for any $x\in X$, there exists some neighbourhood $V(x)$ of $x$ such that the set
    \[
        \left\{\alpha\in A:U_\alpha\cap V(x)\neq\emptyset\right\}
    \]
    is finite.
}

\definition{Definition}{
    A topological space $\{\tau,X\}$ is said to be \textbf{paracompact} if every open cover has a locally finite open refinement.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. $X$ is said to be \textbf{disconnected} if it is the union of at least two disjoint non-empty open sets. Otherwise, $X$ is said to be \textbf{connected}.
}

\theorem{Theorem}{
    A topological space $\{\tau,X\}$ is connected if the only subsets of $X$ which are both open and closed are $\emptyset$ and $X$.
}

\proof{
    The proof is done by contradiction. Let $A\subset X$ be both open and closed, but $A\neq X$ and $A\neq\emptyset$. Then as $A$ is open, there exists a set $B$ such that $B\notin\tau$ ($B$ is closed) and $A\cup B=X$. Hence $B=X\backslash A$. However as $A$ is also closed, there exists a set $C$ such that $C\in\tau$ ($C$ is opne) and $A\cup C=X$. Therefore $C=X\backslash A$. One can see that $B=C$ and we arrive at contradiction $B\notin\tau$ while $C\in\tau$.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. The union $A$ of all connected subsets of $X$ containing a point $x\in X$ is a connected subset of $X$. Then, $A$ is called the \textbf{maximal connected} subset containing $x$ (or \textbf{componet} of $X$ containing $x$), denoted by $C(x)$.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. A \textbf{path} from a point $x\in X$ to a point $y\in X$ in a topological space $X$ is a continuous function $f$ from the unit interval $[0,1]$ to $X$ with $f(0)=x$ and $f(1)=y$.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. A \textbf{path-component} of $X$ is an equivalence class of $X$ under the equivalence relation which makes $x$ equivalent to $y$ if there is a path from $x$ to $y$.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. The space $X$ is said to be \textbf{path-connected} (or pathwise connected or 0-connected) if there is exactly one path-component, i.e. if there is a path joining any two points in $X$.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. A space $X$ is said to be \textbf{arc-connected} or arcwise connected if any two distinct points can be joined by an arc, which by definition is a path $f:[0,1]\to X$ that is also a topological embedding. Explicitly, a path $f:[0,1]\to X$ is called an arc if the surjective map $f:[0,1]\to\operatorname{Im}f$ is a homeomorphism, where its image $\operatorname{Im}f:=f([0,1])$ is endowed with the subspace topology induced on it by $X$.
}

\exmpl{Example}{
    Let $X$ be a finite set with topology $\{\tau,X\}$ that is path-connected. However such space is not arc-connected because there can't be a homeomorphism from an uncountable interval $[0,1]$ to a finite set $X$.
}

\definition{Definition}{
    Let $\{\tau,X\}$ be a topological space. A space is called \textbf{totally disconnected} if its only non-empty  connected subsets consists of single points, i.e. $C(x)=\{x\}$.
}

\theorem{Theorem}{
    Let $\{\tau_i,X_i\},\,i=1,2$ be topological space and let $f:X_1\to X_2$ be a continuous map. If $A\subseteq X_1$ and $A$ is connected, then $f(A)$ is connected.
}

\proof{
}

\theorem{Theorem}{
    Let $\{\tau_i,X_i\},\,i=1,2$ be topological space and let $f:X_1\to X_2$ be a continuous map. If $A\subseteq X_1$ and $A$ is compact, then $f(A)$ is compact.
}

\proof{
}

\theorem{Theorem}{
    Let $\{\tau_i,X_i\},\,i=1,2,3$ be topological space and let $f:X_1\to X_2$ and $g:X_2\to X_3$ be continuous maps. Then the map $g\circ f:X_1\to X_3$ is continuous.
}

\proof{
}

\theorem{Theorem}{
    If a topological space $\{\tau,X\}$ is path-connected, then it is also connected.
}

\proof{
    We do this proof by contradiction. Suppose $X$ is not connected. Then, there exist nonempty disjoint open subsets $U,V\subseteq X$ such that $X=U\cup V$. Pick a point $x\in U$ and a point $y\in V$.\\

    By assumption, there exists a continuous function $f:[0,1]\to X$ such that $f(0)=x$ and $f(1)=y$. Consider the subsets $f^{-1}(U)$ and $f^{-1}(V)$. These are disjoint in $[0,1]$ and their union is $[0,1]$. By the continuity of $f$, they are both open in $[0,1]$. Finally, since $0\in f^{-1}(U)$ and $1\in f^{-1}(V)$, they are both nonempty. We have thus expressed $[0,1]$ as a union of two disjoint nonempty open subsets, a contradiction to the fact that $[0,1]$ is connected. This completes the proof.
}

simply connected

\end{document}
